Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-14 overview.tex
Small change.
dcollins: added MHD-CT overview

\subsubsection{Godunov MUSCL (HD) with Dedner divergence cleaning (MHD)}
This solver was developed by Wang \& Abel to attack problems in
magnetic field amplification during the formation of galaxies
\citep{Wang:2009a} and to understand the role proto-stellar jets for
the theory of star formation \citep{Wang:2009b}. It combines the standard
approach of Godunov \citep{Godunov1959} for finite volume techniques
with the method of lines as described as e.g. by
\cite{leveque2002finite} and \cite{toro-1997}. In addition, however,
it implements the hyperbolic divergence cleaning algorithm of
\cite{2002JCoPh.175..645D}. It supports multiple approximate Riemann
solvers and supports non-ideal equations of states. Consequently,
these suite of solvers can be used for hydro and magneto-hydrodynamic
simulations. It is also this class of solvers as well as a version of
the PPM hydro solver which have been ported to Nvidia's CUDA framework
allowing \enzo to take advantage of modern graphics hardware \citep{Wang:2010}.

\subsubsection{MHD with Constrained Transport (MHD)}

>>>>

\subsubsection{Godunov MUSCL (HD) with Dedner divergence cleaning (MHD)}
This solver was developed by Wang \& Abel to attack problems in
magnetic field amplification during the formation of galaxies
\citep{Wang:2009a} and to understand the role proto-stellar jets for
the theory of star formation \citep{Wang:2009b}. It combines the standard
approach of Godunov \citep{Godunov1959} for finite volume techniques
with the method of lines as described as e.g. by
\cite{leveque2002finite} and \cite{toro-1997}. In addition, however,
it implements the hyperbolic divergence cleaning algorithm of
\cite{2002JCoPh.175..645D}. It supports multiple approximate Riemann
solvers and non-ideal equations of states. Consequently,
these suite of solvers can be used for hydro and magneto-hydrodynamic
simulations. It is also this class of solvers as well as a version of
the PPM hydro solver which have been ported to Nvidia's CUDA framework
allowing \enzo to take advantage of modern graphics hardware \citep{Wang:2010}.

\subsubsection{MHD with Constrained Transport (MHD)}
This MHD method is second order in time and space, and preserves the divergence constraint,
$\nabla \cdot \vecB = 0$, to machine precision through the Constrained Transport
(CT) method.  CT, originally described by \citet{Evans88}, updates the
magnetic field with the curl of an electric field, suitably formulated to
preserve $\nabla \cdot \vecB$.  We employ the CT methods
described by \citet{Balsara99} and \citet{Gardiner05}.  Further, we employ the
second order hyperbolic solver of \citet{Li08} and the divergence free AMR
scheme of \citet{Balsara01}.
